An effective and friendly tool for seed image analysis

### 2021-07-06 extra/response.tex

\documentclass[]{article}

%opening
\title{Response to Comments}
\author{Andrea Loddo, Cecilia Di Ruberto, Mauro Loddo}

\begin{document}

	\maketitle

	We thank the associate editor and reviewers for their constructive comments. 
	We have revised the manuscript according to the suggestions.
	For ease of review, we add a differences PDF file that shows the differences between the original manuscript and the revised version.
	We summarise the major changes below:
	\\
	\begin{enumerate}
		%
		\item We completely reorganised the structure of the manuscript, according to COMPAG guidelines. \\
		\item We removed unnecessary figures, as detailed in the following responses, and updated some figures to provide higher quality and improved descriptions. \\
		\item We added the list of contributions in the Introduction. \\
		\item We highlight the main differences with our first submission.\\
		%
	\end{enumerate}

	\section{Editor}
	\textbf{Whenever possible, please add relevant references from The Visual Computer. It is important to cite related work from the journal you are publishing in.} \\

	\section{Reviewer 1}
	There are not major concerns in the paper. I only suggest two slight modification to improve the work:
	\begin{enumerate}
		\item \textbf{The authors should insert a contribution list at the end of the Introduction so to highlight the real novelties of the papers. According to this, i think the authors should highlight that a DL benchmark is proposed, so to attract more interest in the research community. Also, i would highlight this in the title.} \\

		In the introduction section, we added more details regarding our Deep Learning approach and benchmark. Moreover, we list all the main contributions of our work.  We have also reorganised Sec.3 in order to highlight the deep learning approach and the extensive DL benchmark proposed.

		\item \textbf{A revise of the paper is suggested. Some typos are detected and the writing grammar is quite shallow.} \\
	\end{enumerate}

	We completely revised the English language and corrected the typos.

	\section{Reviewer 2}
	There are not major concerns in the paper. I only suggest two slight modification to improve the work:
	\begin{enumerate}
		\item \textbf{This topic fits the scope of COMPAG, and the content is interesting. However, the paper needs major improvements in writing and organising. The essential criterion of scientific publication should be followed, such as avoiding using first-person too often or redundant descriptions. } \\

		First-person has been removed as much as possible throughout all the manuscript and the redundant descriptions, too.

		\item \textbf{I do suggest the author go through the manuscript thoroughly and carefully check the way of expression. The bottom line is to have the story expressed logically, comprehensively, and concisely. Please reformat the manuscript according to the author's guidelines of the target journal before submission. For COMPAG, the Introduction, methods, and results should be illustrated separately. Some captions of figures and tables are too simple.} \\

		We completely reformatted and reorganised the manuscript, carefully following the COMPAG guidelines. In particular, we organised it with (i) the Introduction section, which introduces the issue and overviews state of the art; (ii) the Materials and Methods section, in which we describe SeedNet, our proposed CNN architecture, the two exploited dataset, and the related preprocessing step; (iii) the Results and discussion section, in which we describe the \textbf{Setup} of all the classification and retrieval experiments, and the metrics used to evaluate the results; the \textbf{Results} of both tasks, the \textbf{Deep learning vs traditional machine learning comparison}, and, finally, we give a complete \textbf{Discussion} of all the obtained results.

		\item \textbf{Revision needs to make and not limited to:\\
			L52-109 Methodology is to illustrate what you did. If not, this should belong to the Introduction. Besides, I suggest the author reorganised the introduction part.}

		We reorganised the Introduction. Now, we introduce the faced issue and then depict the state-of-the-art contributions in this field of study.

		\item \textbf{L193 Consider combining these to images. Figure 7 is potentially a redundant content of Figure 6 or 9}

		We combined previous Fig. 7 into Fig. 6. We now have an only image (Fig. 6) that shows a sample of the local dataset, its related binary mask, and some crop samples.

		\item \textbf{L239 Table 1. I guess this is the layers in sequence? If so, I suggest having another column for Layer \#.}

		A new column has been added in Table 1 for Layer \#.

		\item \textbf{L245 Figure 8. Text is too small to read.}

		We modified the figure by removing the text inside the images and adding it as a subcaption for both figures representing crop samples of the datasets classes (Now: Fig. 7 and 8).

		\item \textbf{L316-340 Large amounts of contents are background introduction and Methodology. Also, consider moving some contents into the introduction section as justification.}

		We moved the information at L316-340, after the reorganisation. We now give some details about the methods and pinpoint the objectives of our comparison in Sec.3.1 (Setup).

		\item \textbf{L351 Table 8. To me, the result of classic approaches is not bad. As you mentioned the time-consuming of DL approaches in Table 3, I'm curious about the performance of the traditional machine learning approaches on time consumption. This could be an advantage of classic machine learning.}

		We added runtimes for traditional classifiers and added a discussion in 3.4:
		\textit{Although the satisfactory results of traditional classifiers, no one outperformed SeedNet.
		CNNs methods generally achieved better performances than the traditional classifiers, which nevertheless had training times less than or equal to a minute. Our proposed model also required 4 and 12 times the training time on the Canadian and local dataset, respectively, even though it outperformed every single compared CNN.
		}

		\item \textbf{L376 Quite a few contents are discussions.}

		We reorganised and extended the discussion section in order to talk about the classification and retrieval results with the proposed network; then, we analysed the results obtained with the other CNNs, to make an exhaustive comparison for both tasks. Finally, we discussed the pros and cons of deep learning vs traditional machine learning methods.

	\end{enumerate}

\end{document}

### 2021-07-12 extra/response.tex

\documentclass[]{article}

%opening
\title{Response to Comments}
\author{Loddo A., Di Ruberto C., \\Vale A.M.P.G.,	Ucchesu M.,	Soares J.M., Bacchetta G.}

@@

\begin{document}

	\maketitle

	We thank the associate editor and reviewers for their constructive comments. 
	We have revised the manuscript according to the suggestions.
	For ease of review, we add a PDF file showing the differences between the original manuscript and the revised version. More precisely, text deleted from the old document (on the left side) and, hence, not in new version is highlighted red. Text added to the new document and, hence, not in the old one is highlighted green.
	We summarise the main changes below:
	\\
	\begin{enumerate}
		%
		\item We have completely reorganised the structure of the manuscript according to the guidelines of The Visual Computer. \\
		\item We have completely revised the English language and corrected typos. \\
		\item We fixed the issues in the bibliography, adapting them to the style of the journal. \\
		\item We have added a detailed comparison with deep learning methods. \\
		\item We have highlighted the main differences with our first presentation. \\
		%
	\end{enumerate}

@@

	\section{Editor}
	\textbf{Whenever possible, please add relevant references from The Visual Computer. It is important to cite related work from the journal you are publishing in.} \\

	We have added several works from The Visual Computer, both in the Introduction and Related work sections, related to the task we have described in this manuscript.

	%%%% Rev 1
	\section{Reviewer 1}
	\begin{enumerate}
	\item \textbf{The literature review is not sufficient. more literature review is needed,} \\
    In the introductory section, we added more details about our approach and the context in which it fits. We have also created Sec.2 to expand on the state of the art, also highlighting traditional and deep learning approaches in plant science.

    \item \textbf{The writing and presentation of the paper have some issues. Please clear the paper.} \\
	We have completely revised the English language and corrected typos. In addition, we have corrected problems in the bibliography, adapting it to the style of the journal.

	\item \textbf{To give better insights to the reader other approaches can be added. Following references can be useful for the same.
	Linear discriminant multi-set canonical correlations analysis (LDMCCA): an efficient approach for feature fusion of finger biometrics.
	Saliency detection based on integrated features
	IoT Security Based on Iris Verification Using Multi-Algorithm Feature Level Fusion Scheme} \\

	We have added a significant section of related work to describe feature fusion approaches, citing those suggested as important examples of improved results.

    \item \textbf{The references are up to date but some are not in the right format.} \\
    We fixed the reference issues, adapting them to the style of the journal.

    \item \textbf{Conclusion section is poor, please improve.} 
    \item \textbf{The conclusions section should conclude that you have achieved from the study, contributions of the study to academics and practices. In addition, list the advantages and disadvantages of the proposed solution, as well as indicate the limitations of work. Further, mention the recommendations of future works.} \\
    We have updated the Conclusion section, giving more emphasis to the pros and cons of the proposed tool. We have included our own contributions in the Introduction and Conclusion sections.

    \item \textbf{Compare your results with the imp methods published in the literature}
    We have compared our approach with those of deep learning in section 5, and in particular in Table 6.

@@

	\end{enumerate}

	\section{Reviewer 4}

	\begin{enumerate}
	\item \textbf{There are some layout problems in this paper. For example, the format of section title and text is same in Abstract, and the table title of Table 4 is under the table.} \\
	Although we have used the only Latex template available for this magazine, we have adapted it to the two-column format, which is closer to the final version once published. In any case, we have followed the official instructions at: https://www.springer.com/journal/371/submission-guidelines.

	\item \textbf{Some descriptions are redundant in this paper. For example, Introduction should be segmented for clarity.} \\
	We completely reformatted and reorganised the manuscript, carefully following the Visual Computer guidelines. In particular, we divided the previous Introduction section, in order to expand the introductory section, as well as the state-of-the-art work, adding more works and describing them in detail. 
	We have completely reformatted and reorganised the manuscript, carefully following Visual Computer guidelines. In particular, we have split the previous Introduction section, in order to expand it, as well as the state of the art, adding more works and describing them in detail. 
	The manuscript is finally organised with: (i) the Introduction section, which introduces the topic; (ii) the Related Work section, which presents the state of the art; (iii) the Materials and Methods section, in which we describe the datasets, the proposed ImageJ plugins, preprocessing, feature extraction and classification steps; (iv) the Results and Discussion section.

	\item \textbf{This paper lacks of visualization results in experimental results.}
	We have added two graphical results in section 5, namely Fig. 8 and 9 to show the results obtained with the different categories of features used.

	\item \textbf{And there is also lacking of comparison experiments with CNN-based methods to prove the effectiveness of the proposed tool.}
	We have compared our approach with those of deep learning in section 5, and in particular in Table 6.

	\item \textbf{For the references, please add more references published in recent years}
	We have created a Related Works section (Section 2) and added several updated works related to the field analysed in this article.
	\end{enumerate}

### 2021-07-12 extra/conflicts.tex
Revisions Round 1

\address{Andrea Loddo\\
	Dept. of Mathematics and Computer Science\\
	University of Cagliari,	09128, Cagliari, Italy \\
	Phone:(+39) 070 675 8503 \\
	Email: \texttt{andrea.loddo@unica.it}}
\signature{Andrea Loddo}

@@

		We would like to submit the paper entitled ``An effective and friendly tool for seed image analysis'' after carefully following your excellent suggestions.
		%
		Below we give the authors biographies.
		%
		\begin{itemize}
		\item Dr. Andrea Loddo is a postdoc researcher at the Dept. of Mathematics and Computer Science, University of Cagliari. He earned his BSc  in 2012, MSc in 2014 and PhD in 2019, all from the University of Cagliari. His Ph.D thesis faced blood cells image analysis and classification issues, for creating automatic diagnosis tools as a support to medical analysis. He is author of 15 scientific manuscripts in peer-reviewed journals and international conference proceedings. His research interests include computer vision, biomedical image analysis, pattern recognition and machine learning. Currently, he is involved in a research project regarding human activity recognition. Moreover, he is pursuing a research activity for crypto scams analysis and biomedical image analysis for diagnosis support systems.
		\item Prof. Dr. Cecilia Di Ruberto received the MS in Computer Science from the University of Salerno, Italy, in 1990 and the Ph.D. degree in Computer Science from the University of Naples, Italy, in 1995. Currently she is Associate Professor of Computer Science at the Department of Mathematics and Computer Science, University of Cagliari, Italy. Her research interests include computer vision, image retrieval, medical image analysis, pattern recognition and machine learning.  She has been working in microscopic image analysis, in particular in blood smear image analysis for cell counting, malaria parasites detection and classification, and leukemia detection. She is author of more than 50 scientific papers in peer-reviewed journals and international conference proceedings.
		\item Dr. Mariano Ucchesu is a postdoctoral researcher at the Centro Conservazione Biodiversità (CCB), Dipartimento di Scienze della Vita e dell’Ambiente (DiSVA), Università degli Studi di Cagliari. He earned his PhD in 2014 from the University of Cagliari. Author of several scientific manuscripts in peer-reviewed journals and international conference proceedings related to this task, his research interests include paleobotanic, seeds analysis, plant science and archeobotanic.
		\item Dr. Prof. Gianluigi Bacchetta is the Coordinator of the Doctorate Course in Environmental and Applied Botany, Vice-coordinator of the Doctorate Course in Earth and Environmental Sciences and Technologies and Vice-Director of the Doctorate School in Engineering and Sciences for the Environment and Territory at the University of Cagliari. Also for the University of Cagliari he is scientific coordinator in the framework of the agreements stipulated with the Universidade de Evora (Evora, Portugal), Universisade do Rio Grande do Norte (Natal, Brasil), University of Tehran (Tehran, Iran), Universitat Jaume I (Castellon, España), Universidad de Castilla la Mancha (Toledo, España), Universitat de Valencia and Universitat Politècnica (Valencia, España).
		\item Dr. Prof.  Alessandra Mendes Pacheco Guerra Vale has a degree in Data Processing from the University Potiguar (1999), Master in Electrical Engineering from the Federal University of Rio Grande do Norte (2002) and PhD in Electrical and Computer Engineering from the Federal University of Rio Grande do Norte (2014). She is currently a professor at the Federal University of Rio Grande do Norte, Escola Agrícola de Jundiaí. She has experience in the area of Information Technology, working mainly on the following topics: intelligent systems, digital image processing, software analysis and development, object orientation, software development process, project management, computer supported cooperative work, database and telemedicine.
		\end{itemize}

>>>>

\address{Andrea Loddo\\
	Dept. of Mathematics and Computer Science\\
	University of Cagliari \\
	09128, Cagliari, Italy \\
	Phone:(+39) 070 675 8503 \\
	Email: \texttt{andrea.loddo@unica.it}}
\signature{Andrea Loddo}

@@

		The authors declare no conflict of interest.
